On the specific recursive structure of iterated parametricity

### 2025-12-04 paper/paper.tex
paper: fix indices in the definition of frames (#5)

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \depstype[n][0,..,p-1]          &        & \defeq            &
    \left(\begin{array}{lll}
              \framep[n][0,...,p-1]   & : & \frametype[n][0,...,p-1]    \\
              \painting[n][0,...,p-1] & : & \paintingtype[n][0,...,p-1]
              (\framep[n][0,...,p-1])                                   \\
              \restrf[n][0,...,p-1]   & : & \restrftype[n][0,...,p-1]
              \left(\begin{array}{l}
                  \framep[n][0,...,p-1]   \\
                  \painting[n][0,...,p-1] \\
                \end{array}\right)                             \\
            \end{array}\right)        \\
    \framep[n+1][0,...,(p+1)-1]     &
    \multicolumn{3}{l}{
    (\deps[n][0,...,p-1]:\depstype[n][0,...,p-1]) :\frametype[n+1][0,...,p]}         \\
    \framep[n+1][0,...,(0+1)-1]     &
    (\unitpoint)                    & \defeq & (\unitpoint,unit)                     \\
    \framep[n+1][0,...,((p+1)+1)-1] &
    \deps[n][0,...,p]               & \defeq &
    \left(\begin{array}{l}
              \framep[n+1][0,...,p]
              (\deps[n][0,...,p-1]), \\
              \Sigma d:\framep[n+1][0,...,p]
              (\deps[n][0,...,p-1])  \\
              \quad \layer[n][p]
              (\deps[n][0,...,p])
              (d)                    \\
            \end{array}\right)                                              \\
    \restrftype[n][0,...,p-1]       &
    \multicolumn{3}{l}{
    \left(\begin{array}{l}
              \framep[n][0,...,p-1]:\frametype[n][0,...,p-1]                             \\
              \painting[n][0,...,p-1]:\paintingtype[n][0,...,p-1](\framep[n][0,...,p-1]) \\
            \end{array}\right) : \U} \\
    \restrftype[n][0,...,0-1]       &
    \left(\begin{array}{l}
              \unitpoint \\
              \unitpoint \\
            \end{array}\right)          & \defeq &
    \unittype                                                                        \\
    \restrftype[n][0,...,(p+1)-1]   &
    \left(\begin{array}{l}
              \framep[n][0,...,p]   \\
              \painting[n][0,...,p] \\
            \end{array}\right)        & \defeq &
    \begin{array}{l}
      \Sigma \restrf[n][0,...,p-1]
      :\restrftype[n][0,...,p-1]
      \left(\begin{array}{l}
                \framep[n+1][0,...,p-1]   \\
                \painting[n+1][0,...,p-1] \\
              \end{array}\right).                     \\
      \Pi q\leq n.\,\Pi \omega.\,\framep[n+1][p]
      \left(\begin{array}{l}
                \framep[n][0,...,p-1]   \\
                \painting[n][0,...,p-1] \\
                \restrf[n][0,...,p-1]   \\
              \end{array}\right) \rightarrow  \framep[n][p] \\
    \end{array}               \\
    \layertype[n][p]                &
    \multicolumn{3}{l}{
      (\deps[n][0,...,p]:\depstype[n][0,...,p])
    : \U}                                                                            \\
    \layertype[n][p]                &
    \deps[n][0,...,p]
                                    & \defeq & \framep[n+1][p]
    (\deps[n][0,...,p-1])
    \rightarrow \U                                                                   \\
    \layer[n][p]                    &
    \multicolumn{3}{l}{
      (\deps[n][0,...,p]:\depstype[n][0,...,p])
      : \layertype[n][p]
      (\deps[n][0,...,p])}
    \\
    \layer[n][p]                    &
    \deps[n][0,...,p]
                                    & \defeq &
    d \mapsto \Pi\omega.\,\painting[n][p](\restrf[n][p](d))                          \\
  \end{array}
\end{equation*}

Later, we shall write $\deps.\framep$, $\deps.\painting$, $\deps.\restrf$ for the projections of a $\deps$. Note that by abuse of notation, we also write $\unitpoint$ for the only inhabitant of $\depstype[n][0,..,0-1]$.

>>>>

\begin{equation*}
  \fontsize{7.2}{9}\selectfont
  \begin{array}{llcl}
    \depstype[n][0,..,p-1]          &        & \defeq            &
    \left(\begin{array}{lll}
              \framep[n][0,...,p-1]   & : & \frametype[n][0,...,p-1]    \\
              \painting[n][0,...,p-1] & : & \paintingtype[n][0,...,p-1]
              (\framep[n][0,...,p-1])                                   \\
              \restrf[n][0,...,p-1]   & : & \restrftype[n][0,...,p-1]
              \left(\begin{array}{l}
                  \framep[n][0,...,p-1]   \\
                  \painting[n][0,...,p-1] \\
                \end{array}\right)                             \\
            \end{array}\right)        \\
    \framep[n+1][0,...,(p+1)-1]     &
    \multicolumn{3}{l}{
    (\deps[n][0,...,p-1]:\depstype[n][0,...,p-1]) :\frametype[n+1][0,...,p]}         \\
    \framep[n+1][0,...,(0+1)-1]     &
    (\unitpoint)                    & \defeq & (\unitpoint,unit)                     \\
    \framep[n+1][0,...,((p+1)+1)-1] &
    \deps[n][0,...,p]               & \defeq &
    \left(\begin{array}{l}
              \framep[n+1][0,...,p]
              (\deps[n][0,...,p-1]), \\
              \Sigma d:\framep[n+1][p]
              (\deps[n][0,...,p-1]).
              \, \layer[n][p]
              (\deps[n][0,...,p])
              (d)                    \\
            \end{array}\right)                                              \\
    \restrftype[n][0,...,p-1]       &
    \multicolumn{3}{l}{
    \left(\begin{array}{l}
              \framep[n][0,...,p-1]:\frametype[n][0,...,p-1]                             \\
              \painting[n][0,...,p-1]:\paintingtype[n][0,...,p-1](\framep[n][0,...,p-1]) \\
            \end{array}\right) : \U} \\
    \restrftype[n][0,...,0-1]       &
    \left(\begin{array}{l}
              \unitpoint \\
              \unitpoint \\
            \end{array}\right)          & \defeq &
    \unittype                                                                        \\
    \restrftype[n][0,...,(p+1)-1]   &
    \left(\begin{array}{l}
              \framep[n][0,...,p]   \\
              \painting[n][0,...,p] \\
            \end{array}\right)        & \defeq &
    \begin{array}{l}
      \Sigma \restrf[n][0,...,p-1]
      :\restrftype[n][0,...,p-1]
      \left(\begin{array}{l}
                \framep[n+1][0,...,p-1]   \\
                \painting[n+1][0,...,p-1] \\
              \end{array}\right).                     \\
      \Pi q\leq n.\,\Pi \omega.\,\framep[n+1][p]
      \left(\begin{array}{l}
                \framep[n][0,...,p-1]   \\
                \painting[n][0,...,p-1] \\
                \restrf[n][0,...,p-1]   \\
              \end{array}\right) \rightarrow  \framep[n][p] \\
    \end{array}               \\
    \layertype[n][p]                &
    \multicolumn{3}{l}{
      (\deps[n][0,...,p]:\depstype[n][0,...,p])
    : \U}                                                                            \\
    \layertype[n][p]                &
    \deps[n][0,...,p]
                                    & \defeq & \framep[n+1][p]
    (\deps[n][0,...,p-1])
    \rightarrow \U                                                                   \\
    \layer[n][p]                    &
    \multicolumn{3}{l}{
      (\deps[n][0,...,p]:\depstype[n][0,...,p])
      : \layertype[n][p]
      (\deps[n][0,...,p])}
    \\
    \layer[n][p]                    &
    \deps[n][0,...,p]
                                    & \defeq &
    d \mapsto \Pi\omega.\,\painting[n][p](\deps.\restrf[n][p][0][\omega](d))                          \\
  \end{array}
\end{equation*}

Note that we write $\deps.\framep$, $\deps.\painting$, $\deps.\restrf$ for the
projections of a $\deps$. Also, by abuse of notation, we write $\unitpoint$ for
the only inhabitant of $\depstype[n][0,..,0-1]$.
